---
title: "Report Group 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center class="anchor" id="Contents" style="background-color:Gainsboro; width:40%;">Contents</center>
* [Contents](#Contents)
* [Introduction](#Introduction)
* [EDA](#EDA)
* [Data Cleaning](#Data Cleaning)
* [Data Manipulation](#Data Manipulation)

<a center class="anchor" id="Introduction" style="background-color:Gainsboro; width:40%;"></a>
<center style="background-color:Gainsboro; width:40%;">Introduction</center>


> 'As part of the course **"Programming in R" at IE - HST**, we foster our newly learned skills by participating in a Kaggle competition. The problem requires us to do Exploratory Data Analysis, Data Cleaning and Manipulation and implement some sort of Machine Learning in R.'

The data can be found  [here](https://www.kaggle.com/c/ams-2014-solar-energy-prediction-contest/overview)

```{r, echo=F}
library(data.table)

rm(list=ls())  #clean environment
#Pierre RDS source
#solar_data <- readRDS('/Documents and Settings/Pierre Computer/Documents/IE_classes/R/group project/solar_dataset.RData')
#Ivan RDS source
#solar_data <- readRDS('C:/Users/Ivan.Polakovic/Desktop/IE/R/group assignment/solar_dataset.RData')
#Max RDS source
solar_data <- readRDS('/Users/admin/OneDrive/Documents/IE - Madrid/Term 1/01 R Programming/Group Assignment/GitHub/data/solar_dataset.RData')
```
```{r, echo=F}
solar_data_dt <- solar_data[,list(solar_data[1:5113,])]
solar_data_predict <- solar_data[,list(solar_data[5114:6909,])]
x_raw_train <- solar_data[1:5113, 2:99] 
x_PC_train <- solar_data[1:5113, 100:456] 
y_train <- solar_data[1:5113, 2:99] 
```


```{r}
summary(solar_data[,1:20])
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
setDT(solar_data_dt)
date_visualization <- solar_data_dt[, .(AVG = rowMeans(.SD)),Date]
scatter.smooth(date_visualization)
```

<a center class="anchor" id="EDA" style="background-color:Gainsboro; width:40%;"></a>
<center style="background-color:Gainsboro; width:40%;">EDA</center>
> 'put **stuff** here'

<a center class="anchor" id="Data Cleaning" style="background-color:Gainsboro; width:40%;"></a>
<center style="background-color:Gainsboro; width:40%;">Data Cleaning</center>
> 'put **stuff** here'

<a center class="anchor" id="Data Manipulation" style="background-color:Gainsboro; width:40%;"></a>
<center style="background-color:Gainsboro; width:40%;">Data Manipulation</center>
> 'put **stuff** here'
